The Globular Cluster System of the Auriga Simulations

### 2019-06-06 AurigaGCS.tex
Copy-pasted some paragraphs from references

@@

>>>>

\citep{2019arXiv190505199C}
``The  mean  and  dispersion  of  GC system MDFs have also been found to scale 
with the mass of the host galaxy over a large range in galaxy mass (Peng et al.
2006). Qualitatively, many galaxies have clearly multi-modal MDF (e.g., Gebhardt
\& Kissler-Patig 1999; Peng et al. 2006; Brodie \&  Strader  2006;  Brodie  et  
al.  2012),  but  the  most massive galaxies typically show broad, single-peaked 
distributions (Harris et al. 2014, 2016, 2017a)''

@@

\citep{2019MNRAS.486.5838R}
``Out of the cluster formation models considered, the `no formation physics' model, 
in which both the CFE and the ICMF are fixed throughout cosmic time, is 
approximately equivalent to those studies  that  use  `particle-tagging' 
techniques  to  identify  GCs  in cosmological simulations (e.g. Tonini 2013, 
Renaud et al. 2017). We find that this cluster formation model continues to form GCs
at a vigorous rate until the present time, which implies it overproduces 
the total GC mass in the Milky Way by a factor
5.5 relative to the mass formed in the fiducial model. Likewise, the continued
formation  of  GCs  in  this  model  predicts  the  on-going  formation
of massive (M $>10^5$ M\Sun) clusters with [Fe/H]< −0.5 should be observed in 
Milky Way-mass galaxies at z=0. For these reasons, an environmentally independent
cluster formation description is not compatible with observations.''
